---
title: "p8105_hw6_js6177"
author: "Jiayi Shi"
date: "2022-11-20"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(patchwork)
library(mgcv)
library(modelr)
library(glmnet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

## Problem 2

The code below imports, cleans, and generally wrangles the data for analysis.
Omit cities Dallas, TX; Phoenix, AZ; Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake; `victim_age` unknown.
```{r}
homicide_data = read_csv("data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    resolved = as.numeric(disposition == "Closed by arrest")
         ) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO","Tulsa, AL")), victim_race %in% c("White", "Black"), victim_age != "Unknown") %>% 
  mutate(
    victim_age = as.numeric(victim_age),
    victim_race = fct_relevel(victim_race, "White")
    )
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. 

```{r}
fit_logistic = 
  homicide_data %>%
  filter(city == "Baltimore") %>% 
  dplyr::select(city_state, resolved, victim_age, victim_race, victim_sex) %>%
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 
```

Obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
# estimate
fit_logistic %>% 
  broom::tidy() %>% 
  mutate(estimate = exp(estimate)) %>% 
  pull(estimate) %>% .[4]

# confidence interval ci
lower_bound = exp(confint(fit_logistic, parm = "victim_sexMale"))[[1]]
upper_bound = exp(confint(fit_logistic, parm = "victim_sexMale"))[[2]]
ci = paste0("(", lower_bound, ",", upper_bound, ")")
```

```{r}
odds_ratio = function(model){
  tibble(
    adjusted_or = model %>% 
      broom::tidy() %>% 
      mutate(estimate = exp(estimate)) %>% 
      pull(estimate) %>% .[4],
    lower_bound = exp(confint(model, parm = "victim_sexMale"))[[1]],
    upper_bound = exp(confint(model, parm = "victim_sexMale"))[[2]],
   )
}
```

```{r message=FALSE}
plot_df = homicide_data %>% 
  dplyr::select(city_state, resolved, victim_age, victim_race, victim_sex) %>% 
  nest(df = resolved:victim_sex) %>% 
  mutate(
    models = map(df, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = .x)),
    results = map(models, odds_ratio)) %>% 
  dplyr::select(-df, -models) %>% 
  unnest(results)
```

Plot
```{r}
plot_df %>% 
  # Organize cities according to the estimated OR.
  mutate(city_state = fct_reorder(city_state, adjusted_or)) %>% 
  
  ggplot(aes(x = city_state, y = adjusted_or))+
  geom_point()+
  geom_errorbar(aes(ymin = lower_bound, ymax = upper_bound))+
  labs(title = "Estimated ORs and CIs for each city", 
       y = "Estimated ORs", 
       x = "City names", 
       caption = "Error bars represent 95% confidence interval") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2, hjust = 1))
```

## Problem 3

Load the data, convert numeric variables `babysex`, `frace`, `malform`, `mrace` to factors and omit missing values.

```{r}
birthwt = read_csv("data/birthweight.csv")
str(birthwt)
```

```{r}
birthwt = birthwt %>% 
  mutate(across(c(babysex, frace, malform, mrace), as.factor)) %>% 
  select(bwt, everything()) 

#First ensure that the missing values have been removed from the data
birthwt = na.omit(birthwt)

#sapply(birthwt, function(x) sum(is.na(x)))# no missing values
```

I build my model `both` using stepwise regression. 

```{r}
null = lm(bwt ~ 1, data = birthwt)
full = lm(bwt ~ ., data = birthwt)
both = step(null, direction='both', scope=formula(full), trace=0)
both$coefficients
```

Plot of model residuals against fitted values:

```{r}
birthwt %>% 
  add_predictions(both) %>% 
  add_residuals(both) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = .5)
```

I then compare my model to two others. I make a violin plot to get a sense of variance in prediction error to show prediction error distributions across methods. My model is a clear winner.

```{r}
cv_df = 
  crossv_mc(birthwt, 100) %>% 
  mutate(
    my_mod  = map(train, ~both, data = .x),
    mod_1  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_2  = map(train, ~lm(bwt ~ bhead*blength*babysex, data = .x))) %>% 
  mutate(
    rmse_mymod = map2_dbl(my_mod, test, ~rmse(model = .x, data = .y)),
    rmse_mod1 = map2_dbl(mod_1, test, ~rmse(model = .x, data = .y)),
    rmse_mod2 = map2_dbl(mod_2, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```


